---
title: Math Geeks + Ryan 
output: 
  ioslides_presentation:
    widescreen: true
    smaller: true
  center: true
---

## Bargraph of Age vs Y
```{r echo=FALSE, out.width = "90%"}
setwd("~/Documents/GitHub/OCRugVARKS/data")
data <- read.csv("bank-full.csv", TRUE, ';')
colory <- "#56a8e8"
colorn <- "grey75"  

library(ggplot2)
ggplot(data, aes(age, fill = y)) + geom_bar() +
  theme_minimal() + scale_fill_manual(values = c(colorn,colory)) +
  labs(title = NULL, 
  x = "Age",
  y = "Number of Persons Called",
  fill = "Subscribed?") +
  guides(fill = guide_legend(reverse = TRUE))
``` 
 
```{r echo = FALSE, out.width = "90%"}
## Bargraph of percentages of Age vs Y
suppressWarnings(print(ggplot(data, aes(age, fill = y)) + geom_bar(position = "fill") +
  theme_minimal() + scale_fill_manual(values = c(colorn,colory)) +
  labs(title = NULL, 
  x = "Age",
  y = "Number of Persons Called",
  fill = "Subscribed?") +
  xlim(18,95) +
  guides(fill = guide_legend(reverse = TRUE))))
```



## Bargraph of Jobs vs Y
```{r}
ggplot(data, aes(job, fill = y)) + coord_flip()  + geom_bar() +
   theme_minimal() + scale_fill_manual(values = c(colorn,colory)) +
  labs(title = NULL, 
  x = "Jobs",
  y = "Number of Persons Called",
  fill = "Subscribed?") +
  guides(fill = guide_legend(reverse = TRUE))
```

## Bargraph of Martial status vs Y
```{r}
ggplot(data,aes(marital, fill = y)) + geom_bar() +
  geom_text(stat = 'count', aes(label = ..count.., vjust = -0.2)) +
  theme_minimal() + scale_fill_manual(values = c(colorn,colory)) +
  labs(title = NULL, 
  x = "Maritial Status",
  y = "Number of Persons Called",
  fill = "Subscribed?") +
  guides(fill = guide_legend(reverse = TRUE))
#no significance
```

## Bargraph of education vs Y
```{r}
ggplot(data,aes(education, fill = y)) + geom_bar() + 
  theme_minimal() + scale_fill_manual(values = c(colorn,colory)) +
  labs(title = NULL, 
  x = "Education Level",
  y = "Number of Persons Called",
  fill = "Subscribed?") +
  guides(fill = guide_legend(reverse = TRUE))
summary(data$education)
```

## Bargraph of default vs Y
```{r}
ggplot(data,aes(default, fill = y)) + geom_bar(position = "fill") +
  theme_minimal() + scale_fill_manual(values = c(colorn,colory)) +
  labs(title = NULL, 
  x = "If Defaulted Bank Loans",
  y = "Number of Persons Called",
  fill = "Subscribed?") +
  guides(fill = guide_legend(reverse = TRUE))
```
### Those who defaulted should not be called. This is a waste of money

## bargraph of housing vs Y
```{r}
ggplot(data, aes(housing, fill = y)) + geom_bar() +
    theme_minimal() + scale_fill_manual(values = c(colorn,colory)) +
  labs(title = NULL, 
  x = "If House Loans were Taken",
  y = "Number of Persons Called",
  fill = "Subscribed?") +
  guides(fill = guide_legend(reverse = TRUE))
```

## bargraph of loan vs Y
```{r}
ggplot(data, aes(loan, fill = y)) + geom_bar(position = "fill") +
    theme_minimal() + scale_fill_manual(values = c(colorn,colory)) +
  labs(title = NULL, 
  x = "If Any Loans Taken",
  y = "Number of Persons Called",
  fill = "Subscribed?") +
  guides(fill = guide_legend(reverse = TRUE))
```
## no significance

## bargraph of contact vs Y
```{r}
ggplot(data, aes(contact, fill = y)) + geom_bar(position = "fill") +
    theme_minimal() + scale_fill_manual(values = c(colorn,colory)) +
  labs(title = NULL, 
  x = "Types of Contacts",
  y = "Number of Persons Called",
  fill = "Subscribed?") +
  guides(fill = guide_legend(reverse = TRUE))
summary(data$contact)
```

## bargraph of campaign vs Y
```{r}
ggplot(data, aes(campaign, fill = y)) +geom_bar() +
    theme_minimal() + scale_fill_manual(values = c(colorn,colory)) +
  labs(title = NULL, 
  x = "Number of Calls for a Person",
  y = "Number of Persons Called",
  fill = "Subscribed?") +
  guides(fill = guide_legend(reverse = TRUE)) + 
  xlim(0,15)
```
#if the person doesn't say yes within the first three times, then the bank is wasting money and effort on calling again

## bargraph of number of days since previously contacted vs Y
```{r}
ggplot(data,aes(pdays, fill = y)) + geom_bar() + xlim(0,300) +
    theme_minimal() + scale_fill_manual(values = c(colorn,colory)) +
  labs(title = NULL, 
  x = "Number of Days Inbetween Consecutive Calls",
  y = "Number of Persons Called",
  fill = "Subscribed?") +
  guides(fill = guide_legend(reverse = TRUE))
```

## bargraph of number of contacts in a prior campaign vs Y
```{r}
ggplot(data,aes(previous, fill = y)) + geom_bar(position = "dodge") + 
    theme_minimal() + scale_fill_manual(values = c(colorn,colory)) +
  labs(title = NULL, 
  x = "Number of Calls in Prior Campaigns",
  y = "Number of Persons Called",
  fill = "Subscribed?") +
  guides(fill = guide_legend(reverse = TRUE)) +
  xlim(-1,10)
```

